Arrows for Parallel Computations

### 2018-01-05 paper/content/benchmarks.tex
fixed minor unclear statement in benchmark.tex

For Sudoku the situation is slightly different. There is a minimal significant ($-1.4\% \; \pm 1.2\%$ at 8 cores) speed improvement with PArrows Eden~CP version when compared with the base Eden CP benchmark. However, with increasing number of cores the error margin reaches zero again: $-1.6\% \; \pm 5.0\%$ at 16 cores. The |Par| Monad shows a similar development, \eg with $-1.95\% \; \pm 0.64\%$ at 8 cores. The GpH version shows both a significant speed \textit{improvement} from PArrows of $-4.2\% \; \pm 0.26\%$ and a minor overhead of $0.87\% \; \pm 0.70\%$. \mbcomment{Widerspricht sich das nicht?}

>>>>

For Sudoku the situation is slightly different. There is a minimal significant ($-1.4\% \; \pm 1.2\%$ at 8 cores) speed improvement with PArrows Eden~CP version when compared with the base Eden CP benchmark. However, with increasing number of cores the error margin reaches zero again: $-1.6\% \; \pm 5.0\%$ at 16 cores. The |Par| Monad shows a similar development, \eg with $-1.95\% \; \pm 0.64\%$ at 8 cores. The GpH version shows both a significant speed \textit{improvement} from PArrows of $-4.2\% \; \pm 0.26\%$ (for 16 cores) and a minor overhead of $0.87\% \; \pm 0.70\%$ (4 cores).
